This chapter shows how the functional and non-functional requirements of the eMALL system described in the RASD are met.
Firstly, we describe the mapping between the requirements listed in the 3.2.1 \textit{Requirements} section in the RASD
and the components identified in section 2.2 of this document.
Then, we comment on how \textit{Performance Requirements} and \textit{Software System Attributes} described in the 3.3
and 3.5 sections of the RASD are met thanks to the design adopted for the eMALL system.


\section{Functional Requirements Traceability}
\label{sec: functional_requirements_traceability}%
The following table lists all the requirements that are satisfied by the components.
Texts of the requirements are inserted in the table to facilitate comprehension.
\begin{center}
    \begin{longtable}{p{0.3\linewidth}p{0.7\linewidth}}
        \hline
        Registration Service                   & R1. The eMALL system shall allow an unregistered EVD to create an account.                                                                      \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        EVD Authentication Service             & R2. The eMALL system shall allow a registered EVD to log in.                                                                                    \\
        \hline
        EVD Profile Manager Service            & R3. The eMALL system shall allow a registered EVD to add an EV in his profile.                                                                  \\
        & R21.\ The eMALL system shall allow a registered EVD to insert a new payment method.                                                             \\
        & R22.\ The eMALL system shall allow a registered EVD to select a payment method.                                                                 \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        Explore Stations Service               & R8. The eMALL system shall allow a registered EVD to get all the charging station near to his current location.                                 \\
        & R9. The eMALL system shall allow a registered EVD to insert a specific location to get charging station nearby.                                 \\
        & R10.\ The eMALL system shall allow a registered EVD to move into the map of charging stations.                                                  \\
        & R11.\ The eMALL system shall allow a registered EVD to select a specific charging station.                                                      \\
        & R12.\ The eMALL system shall allow a registered EVD to get the location of a specific charging station.                                         \\
        & R13.\ The eMALL system shall allow a registered EVD to get the costs of a specific charging station.                                            \\
        & R14.\ The eMALL system shall allow a registered EVD to get the CPO owner of a specific charging station.                                        \\
        & R15.\ The eMALL system shall allow a registered EVD to get type of connectors of a specific charging station.                                   \\
        & R16.\ The eMALL system shall allow a registered EVD to get maximum power supply of the spots of a specific charging station.                    \\
        & R17.\ The eMALL system shall allow a registered EVD to get the status of a specific charging station.                                           \\
        \hline
        Booking Service                        & R5. The eMALL system shall allow a registered EVD to book a charge.                                                                             \\
        & R6. The eMALL system shall allow a registered EVD to select a timeframe to reserve a charging point.                                            \\
        & R55.\ The eMALL system shall reserve a charging point in a certain timeframe.                                                                   \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        Manage Charging Session Service        & R25.\ The eMALL system shall allow a registered EVD to start a charging process.                                                                \\
        & R26.\ The eMALL system shall verify the identity of the EVD requesting to start a charging session.                                             \\
        & R32.\ The eMALL system shall send notifications about the current status of the charging session to the registered EVD.                         \\
        & R33.\ The eMALL system shall allow a registered EVD to stop the charging session.                                                               \\
        & R35.\ The eMALL system shall send the receipt of the charging session to the registered EVD.                                                    \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        Promotion Service                      & R18.\ The eMALL system shall allow a registered EVD to get the list of active promotions.                                                       \\
        & R19.\ The eMALL system shall allow a registered EVD to select a specific promotion.                                                             \\
        & R20.\ The eMALL system shall allow a registered EVD to activate a promotion.                                                                    \\
        \hline
        Calendar Service                       & R7. The eMALL system shall add a booked reservation into EVD’s calendar.                                                                        \\
        & R37.\ The eMALL system shall allow a registered EVD to access in his own calendar.                                                              \\
        & R38.\ The eMALL system shall allow a registered EVD to add a new activity into his calendar.                                                    \\
        & R39.\ The eMALL system shall allow a registered EVD to specify the starting hour of a new activity.                                             \\
        & R40.\ The eMALL system shall allow a registered EVD to specify the destination of a new activity.                                               \\
        & R41.\ The eMALL system shall save a new activity into EVD’s calendar.                                                                           \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        Suggestion Service                     & R4. The eMALL system shall communicate with EV’s brand API to get needed information.                                                           \\
        & R42.\ The eMALL system shall calculate the best schedules of where and when to charge registered EVD’s EV so to minimize costs and wasted time. \\
        & R43.\ The eMALL system shall communicate to the registered EVD the details of the suggestions about the calculated schedules.                   \\
        \hline
        Payment Service                        & R23.\ The eMALL system shall allow a registered EVD to pay with the preferred payment method.                                                   \\
        & R24.\ The eMALL system shall communicate with third-party payment services to make the payments.                                                \\
        & R36.\ The eMALL system shall communicate the outcome of the payment to a registered EVD.                                                        \\
        \hline
        CPO Authentication Service             & R44.\ The eMALL system shall allow a CPO to log in as a business user.                                                                          \\
        &                                                                                                                                                 \\
        \hline
        CPO Profile Manager Service            & R66.\ The eMALL system shall allow a CPO to update its electricity provider.                                                                    \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        & R70.\ The eMALL system shall allow the CPO to manage its company personal information.                                                          \\
        \hline
        Charging Station Manager Service       & R45.\ The eMALL system shall allow a CPO to manage its charging stations.                                                                       \\
        & R46.\ The eMALL system shall allow a CPO to set new selling prices for charging sessions.                                                       \\
        & R47.\ The eMALL system shall allow a CPO to add a new charging station in its profile.                                                          \\
        & R48.\ The eMALL system shall allow a CPO to specify the location of charging station (region, province, city, address).                         \\
        & R49.\ The eMALL system shall allow a CPO to specify the status of a charging station (available, maintenance, broken, unavailable).             \\
        & R50.\ The eMALL system shall allow a CPO to add a charging point in an existing charging station.                                               \\
        & R51.\ The eMALL system shall allow a CPO to specify the serial number of charging point.                                                        \\
        & R52.\ The eMALL system shall allow a CPO to specify the types of connectors of a charging point.                                                \\
        & R53.\ The eMALL system shall allow a CPO to specify the maximum power of a charging point.                                                      \\
        & R54.\ The eMALL system shall allow a CPO to specify the type of connectors of a charging point.                                                 \\
        & R61.\ The eMALL system shall allow a CPO to schedule a maintenance session for a charging station.                                              \\
        & R62.\ The eMALL system shall allow a CPO to specify date and starting hour of a maintenance session for a charging station.                     \\
        & R69.\ The eMALL system shall store users information.                                                                                           \\
        \hline
        Charging Station Communication Service & R28.\ The eMALL system shall communicate to charging points to start the charging session.                                                      \\
        & R29.\ The eMALL system shall define the source of the charging session (batteries or DSO).                                                      \\
        & R30.\ The eMALL system shall define the power of the charging session.                                                                          \\
        & R31.\ The eMALL system shall get EV’s battery status.                                                                                           \\
        & R34.\ The eMALL system shall communicate to a charging point to stop the charging session.                                                      \\
        & R63.\ The eMALL system shall communicate to a charging station to schedule a maintenance at a specified timeframe.                              \\
        \hline
        Promotion Manager Service              & R56.\ The eMALL system shall allow a CPO to manage its promotions.                                                                              \\
        & R57.\ The eMALL system shall allow a CPO to create a new promotion.                                                                             \\
        & R58.\ The eMALL system shall allow a CPO to specify the details of the a promotion.                                                             \\
        & R59.\ The eMALL system shall save the information of a promotion.                                                                               \\
        & R60.\ The eMALL system shall initialize the information of a new promotion.                                                                     \\
        \hline
        DSO Manager Service                    & R64.\ The eMALL system shall allow a CPO to get the list of DSOs.                                                                               \\
        & R65.\ The eMALL system shall allow a CPO to select a DSO from the list of DSOs.                                                                 \\
        & R67.\ The eMALL system shall communicate to a specified DSO to send energy to the charging stations of a CPO.                                   \\
        & R68.\ The eMALL system shall get the electricity selling prices from the DSOs.                                                                  \\
        \hline
        \caption{Mapping between components and requirements.}
        \label{tab: map_comp_req}%
    \end{longtable}
\end{center}

\newpage


\section{Non Functional Requirements Traceability}
\label{sec: non_functional_requirements_traceability}%

\subsection{Performance Requirements}
\label{subsec:performance_requirements}%
The \textit{Number of users} section (3.3 of the RASD) says that the system should be able to handle $50\ 000$ users.
The performance requirement is guaranteed thanks to the adopted of a microservices architecture and
the insertion of a load balancer to distribute requests into the several nodes that constitute the system.
In this way, the system avoids cases of network congestion. \\
From the time response point of view, there are not strict performance requirements.
According to the relations explained in the previous sections, there are not complex communications, so the time needed
by the \verb|eMALL| system to answer to received requests won't be high.

\subsection{Software System Attributes}
\label{subsec:software_system_attributes}%
Thanks to loose coupling considered for the identification of services, when a module fails the rest of the system keeps running.
In this way, the availability of the system is guaranteed.
When a module fails, it is not necessary to halt the whole system to proceed with the maintenance session:
only the service in question will be maintained, the other ones won't be influenced.
Finally, the system guarantees security for users information encrypting them before proceeding with the storage
and memorizing all the data on the server side.
The client, as already explained in the 2.7.3 section will be a thin client, so its purpose is to communicate with services
interfaces and sending requests to the server, that will handle any insertion, update or deletion of data.